%==============================================================
%  MANVENDRA RAJPOOT — COVER LETTER (company-agnostic)
%
%  COMPILER: LuaLaTeX (required for the Carlito/Calibri font).
%    - Overleaf: Menu (top-left) -> Compiler -> LuaLaTeX
%    - Local:    lualatex Manvendra_Rajpoot_CoverLetter.tex
%  Compiling with plain pdflatex falls back to Helvetica.
%
%  FONT: Carlito = Google's metric-identical clone of Calibri.
%  Identical preamble to the resume so the two documents match.
%
%  This version is generic: no company name, no role source, no
%  bracketed placeholders. Send as-is. It fills a full A4 page,
%  with the only whitespace being the 0.5in margin on all sides.
%==============================================================
\documentclass[11pt,a4paper]{article}

% ---------- layout ----------
\usepackage[margin=0.5in]{geometry}

% ---------- font: Carlito (Calibri clone) via LuaLaTeX ----------
\usepackage{iftex}
\ifPDFTeX
  % FALLBACK ONLY (pdflatex cannot load Carlito) — use LuaLaTeX!
  \usepackage[T1]{fontenc}
  \usepackage{helvet}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage{fontspec}
  \setmainfont{Carlito}
\fi

\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\definecolor{subtlegray}{HTML}{555555}
\definecolor{rulecolor}{HTML}{999999}
\usepackage[colorlinks=true,urlcolor=black,linkcolor=black,citecolor=black]{hyperref}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\linespread{1.32}\selectfont

% no hyphenation + ragged right: even word spacing, whole tech terms
\hyphenpenalty=10000
\exhyphenpenalty=50
\usepackage[document]{ragged2e}
\setlength{\RaggedRightParindent}{0pt}
\emergencystretch=3em

% ---------- body paragraph spacing ----------
\setlength{\parskip}{11pt}

% only ONE role variable — edit if the title differs, otherwise leave it
\newcommand{\RoleTitle}{Backend Developer}

\begin{document}

% ---------- header: identical to the resume ----------
\noindent
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{}}
  \begin{tabular}[c]{@{}l@{}}\small
    \href{mailto:manvendra@rajpoot.dev}{manvendra@rajpoot.dev}\\[1pt]
    \small +91 94522 77560
  \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}
    {\fontsize{24}{26}\selectfont\bfseries Manvendra Rajpoot}\\[4pt]
    {\color{subtlegray}\href{https://rajpoot.dev}{rajpoot.dev}}
  \end{tabular} &
  \begin{tabular}[c]{@{}r@{}}\small
    \href{https://github.com/alzywelzy}{github.com/alzywelzy}\\[1pt]
    \small \href{https://rajpoot.dev/linkedin}{linkedin.com/in/alzywelzy}
  \end{tabular}
\end{tabular*}
\vspace{2pt}
{\color{rulecolor}\rule{\textwidth}{0.4pt}}

\vspace{22pt}

Dear Hiring Manager,

% ---------- body ----------
I am writing to apply for the \RoleTitle{} role on your team. I build and own
backend systems where correctness is not optional: platforms that move money,
provision infrastructure, enforce access, and stay observable when they are under
load. Across two roles I have taken these systems from architecture to production,
and the work below is the kind I want to keep doing at greater scale.

Most recently, at CloudTechTiq, I architected a multi-tenant hosting and billing
platform on Django REST Framework spanning more than 25 apps and 230 ViewSets under a
single unified API. The part I am most confident about is the money path. I designed a
dual-gateway payment system across Razorpay and Stripe with HMAC-SHA256 webhook
idempotency to stop duplicate charges, wired end-to-end through invoicing,
provisioning, and double-entry ledger reconciliation, plus Indian GST e-invoicing
against the NIC gateway with IRN generation and signed QR codes. Billing is
unforgiving work where a single silent error compounds into real financial damage, and
I have shipped it correctly in production.

The platform also required the full supporting system that a serious product depends
on, and I built it. That includes RS512 JWT authentication with kid-keyed JWKS and
refresh-token rotation over HTTPOnly cookies, a two-factor flow over email OTP and TOTP,
and a 43-permission department-scoped role-based access system. On top of that I shipped
real-time notifications over a Django Channels and Redis WebSocket server with
JWT-authenticated async consumers, backed by a 24-task Celery system with late
acknowledgement and worker-lost requeue. I care about performance under scale as much as
correctness, so I eliminated N+1 queries across a dual async and sync database layer, and
I set up end-to-end observability with OpenTelemetry tracing across a Prometheus,
Grafana, Loki, and Tempo stack so that a failure anywhere traces back to a single
request. I ship this work through multi-stage Docker builds and a GitHub Actions pipeline
rather than leaving it on my machine, and I open-sourced a type-safe Namecheap SSL and
domain SDK to PyPI along the way.

Earlier, at Radixlink, I built Rosterly, a multi-tenant workforce and payroll SaaS on
Django and FastAPI with schema-per-tenant isolation via django-tenants. I owned the full
timesheet-to-payroll-to-invoicing lifecycle, including atomic multi-assignment timesheet
processing, automated payroll reconciliation on approval, Plaid bank-account aggregation
with transaction sync and duplicate filtering, and multi-format financial reporting in
PDF, Excel, and CSV. Across both roles the throughline is the same: I take ownership of
complex, correctness-critical backend systems and make them reliable, observable, and
maintainable.

I would welcome the opportunity to discuss how my experience can contribute to your
team, and I am happy to walk through any of the systems above in more technical detail.
Thank you for your time and consideration.

\vspace{\stretch{0.5}}

Sincerely,\\[6pt]
Manvendra Rajpoot

\end{document}
