%==============================================================
%  MANVENDRA RAJPOOT — RESUME
%
%  COMPILER: XeLaTeX (required for the Carlito/Calibri font).
%    - Overleaf: Menu (top-left) -> Compiler -> XeLaTeX
%    - Local:    xelatex Manvendra_Rajpoot_Resume.tex
%  Compiling with plain pdflatex falls back to Helvetica.
%
%  FONT: Carlito = Google's metric-identical clone of Calibri.
%  Same widths, same look, legally embeddable. If you compile on
%  a machine with real Calibri installed, you can change
%  \setmainfont{Carlito} to \setmainfont{Calibri}.
%
%  HOW TO EDIT:
%   - Job:      \entry{Role}{Company}{Dates} + itemize block
%   - Project:  \project{Name}{display-url}{full-url} + itemize
%   - Skills:   \item \textbf{Label:} items
%   - Escaping: \& for "&", \% for "%", -- for date dashes
%==============================================================
\documentclass[11pt,a4paper]{article}

% ---------- layout ----------
\usepackage[margin=0.5in]{geometry}

% ---------- font: Carlito (Calibri clone) via XeLaTeX ----------
\usepackage{iftex}
\ifPDFTeX
  % FALLBACK ONLY (pdflatex cannot load Carlito) — use XeLaTeX!
  \usepackage[T1]{fontenc}
  \usepackage{helvet}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage{fontspec}
  \setmainfont{Carlito}
\fi

\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\definecolor{subtlegray}{HTML}{555555}
\usepackage[colorlinks=true,urlcolor=black,linkcolor=black,citecolor=black]{hyperref}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\linespread{0.99}\selectfont

% no hyphenation + ragged right: even word spacing, whole tech terms
\hyphenpenalty=10000
\exhyphenpenalty=50
\usepackage[document]{ragged2e}
\setlength{\RaggedRightParindent}{0pt}
\emergencystretch=3em

% ---------- section style: bold + full-width rule (as in sample) ----------
\titleformat{\section}
  {\bfseries\large}{}{0pt}
  {}
  [\vspace{-6pt}{\color{rulecolor}\rule{\textwidth}{0.4pt}}]
\titlespacing*{\section}{0pt}{3pt}{2.4pt}
\definecolor{rulecolor}{HTML}{999999}

% ---------- tight bullets ----------
\setlist[itemize]{label=\textbullet, leftmargin=0.2in,
                  itemsep=1.6pt, parsep=0pt, topsep=1.8pt,
                  before=\RaggedRight}

% ---------- reusable macros ----------
% \entry{Role}{Company}{Dates} : three-column bold row
\newcommand{\entry}[3]{%
  \vspace{4.5pt}\noindent\textbf{#1}\hfill\textbf{#2}\hfill{\color{subtlegray}#3}\par\vspace{2pt}}

% \project{Name}{display-url}{full-url}
\newcommand{\project}[3]{%
  \vspace{4pt}\noindent\textbf{#1}\hfill
  {\small\color{subtlegray}\href{#3}{\texttt{#2}}}\par\vspace{2pt}}

%==============================================================
\begin{document}

% ---------- header: full-width table, columns take natural width ----------
% tabular* with \extracolsep{\fill}: side blocks hug the margins, the
% stretch glue absorbs all slack, so nothing is squeezed.
\noindent
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r@{}}
  \begin{tabular}[c]{@{}l@{}}\small
    \href{mailto:manvendra@rajpoot.dev}{manvendra@rajpoot.dev}\\[1pt]
    \small +91 94522 77560
  \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}
    {\fontsize{24}{26}\selectfont\bfseries Manvendra Rajpoot}\\[4pt]
    {\color{subtlegray}\href{https://rajpoot.dev}{rajpoot.dev}}
  \end{tabular} &
  \begin{tabular}[c]{@{}r@{}}\small
    \href{https://github.com/alzywelzy}{github.com/alzywelzy}\\[1pt]
    \small \href{https://rajpoot.dev/linkedin}{linkedin.com/in/manvendra}
  \end{tabular}
\end{tabular*}
\vspace{1pt}

% ---------- experience ----------
\section{Experience}

\entry{Backend Developer}{CloudTechTiq}{Nov 2024 -- Present}
\begin{itemize}
  \item Architected a multi-tenant hosting and billing/ERP SaaS on \textbf{Django
        REST Framework} spanning 25+ apps and 230+ ViewSets under a unified
        \texttt{/api/} namespace.
  \item Designed a dual-gateway payment system (\textbf{Razorpay} +
        \textbf{Stripe}) with HMAC-SHA256 webhook idempotency to prevent duplicate
        charges, coordinating payment, invoicing, provisioning, and double-entry
        ledger reconciliation, plus Indian GST e-invoicing (EINV-2.1) through the
        NIC gateway with IRN generation and signed QR codes.
  \item Secured the platform with RS512 \textbf{JWT} auth (kid-keyed JWKS,
        refresh-token rotation over HTTPOnly cookies), a 2FA flow over email OTP
        and RFC-6238 TOTP, and a 43-permission department-scoped RBAC.
  \item Shipped real-time notifications over a \textbf{Django Channels} 4 + Redis
        WebSocket server with JWT-authenticated async consumers, backed by a
        24-task \textbf{Celery} system (late-ack, worker-lost requeue).
  \item Eliminated N+1 queries via Prefetch/OuterRef/Exists across a dual
        async/sync database layer (asyncpg + psycopg) on SQLAlchemy 2.0 with
        connection pooling and keyset cursor pagination.
  \item Built a service-provisioning engine that tracks each order through its
        lifecycle across seven service types, automating bare-metal setup over an
        HPE iLO Redfish wrapper and Celery-driven IP allocation.
  \item Set up end-to-end observability with \textbf{OpenTelemetry} tracing and a
        Prometheus/Grafana/Loki/Tempo stack, so failures across services could be
        traced to a single request.
  \item Built and open-sourced a type-safe Namecheap SSL/domain SDK
        (\textbf{httpx}, \textbf{Pydantic v2}, mypy-strict), published to PyPI ---
        \href{https://github.com/alzywelzy/namecheap-wrapper}{github.com/alzywelzy/namecheap-wrapper}.
  \item Containerized and shipped the platform through multi-stage Docker images
        and a GitHub Actions pipeline publishing to GHCR.
\end{itemize}

\entry{Backend Developer}{Radixlink}{Jun 2023 -- Sep 2024}
\begin{itemize}
  \item Built Rosterly, a multi-tenant workforce/payroll SaaS (\textbf{Django} 4.2
        + \textbf{FastAPI}, 16 apps, 237 REST endpoints) with schema-per-tenant
        isolation via \textbf{django-tenants}.
  \item Developed the timesheet \texttt{->} payroll \texttt{->} invoicing
        lifecycle with atomic multi-assignment timesheet processing and automated
        payroll reconciliation on approval, eliminating N+1s on large payroll runs.
  \item Integrated \textbf{Plaid} bank-account aggregation with transaction sync
        and duplicate filtering across all tenant schemas, scheduled via
        \textbf{Celery} Beat.
  \item Modeled polymorphic assignments (C2C/FTE/T\&M) with date-range conflict
        detection and a temporal pay-rate system with effective-date ranges and
        overlap validation.
  \item Generated multi-format financial reporting (PDF/Excel/CSV) with WeasyPrint
        and Pandas, plus transaction-protected sequential PDF invoice numbering.
\end{itemize}

% ---------- education ----------
\section{Education}
\entry{Bachelor of Computer Applications (BCA)}{Bundelkhand University}{Jul 2021 -- Jun 2024}
\begin{itemize}
  \item Built an AI-powered news summarizer in Python as a final-year academic
        project, using the OpenAI API to condense full-length articles into short,
        readable digests.
\end{itemize}

% ---------- skills ----------
\section{Technical Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, SQL, TypeScript, JavaScript, Bash
  \item \textbf{Backend:} Django, Django REST Framework, FastAPI, Celery,
        SQLAlchemy, Pydantic, asyncio, WebSockets, SSE, REST, GraphQL
  \item \textbf{Data \& Infra:} PostgreSQL, Redis, MongoDB, MySQL, Alembic,
        RabbitMQ; AWS (EC2, S3, RDS, Lambda), Azure, Apache CloudStack, Docker,
        Kubernetes, GitHub Actions, GHCR, Gunicorn, NGINX, Linux
  \item \textbf{Security \& Payments:} OAuth2/OpenID, JWT, RBAC, MFA, 2FA/TOTP,
        HMAC, Stripe, Razorpay, Plaid
  \item \textbf{AI, Observability \& Testing:} OpenAI API, LangChain;
        OpenTelemetry, Prometheus,
        Grafana, Sentry, pytest, TDD, Unit/Integration/E2E, CI/CD, Agile/Scrum
\end{itemize}

\end{document}
